\documentclass[10pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}
  {\large\bfseries}
  {}
  {0pt}
  {}

\begin{document}

% Header

{\LARGE \textbf{Rivaldo Silalahi}}\\[2pt]
\textit{Site Reliability Engineer / Cloud Native \& Observability}\\[4pt]

\href{mailto:rivaldosilalahi13@gmail.com}{rivaldosilalahi13@gmail.com} \quad|\quad
\href{tel:PHONE_NUMBER_PLACEHOLDER}{PHONE_NUMBER_PLACEHOLDER} \quad|\quad
Samosir, North Sumatera, Indonesia\\
\href{https://www.linkedin.com/in/rivaldo-silalahi/}{linkedin.com/in/rivaldo-silalahi} \quad|\quad
\href{https://github.com/IDiot29}{github.com/IDiot29}

% Summary

\section*{Summary}

Site Reliability Engineer with 3+ years of experience building and operating cloud-native platforms, observability stacks and AI inference infrastructure on Kubernetes (EKS, k3s), AWS and GCP. 
Focus areas: SRE, DevSecOps, GitOps and AI infra --- designing centralized metrics/logs/traces, standardizing reliability practices and running GPU-based LLM inference with vLLM and SGLang.
Strong bias toward automation (Terraform, NixOS, GitOps) and reducing operational toil for engineering teams.

% Skills

\section*{Skills}

\textbf{SRE \& Observability}: Prometheus, Cortex, VictoriaMetrics, ELK, OpenTelemetry, Grafana, Loki\\
\textbf{Cloud Native \& OS}: Linux, NixOS, Kubernetes (EKS, k3s, Kubespray), Helm, Flux, Argo CD, Docker, AWS, GCP\\
\textbf{DevSecOps \& Platform}: Terraform, Ansible, Packer, Nix, CI/CD (Google Cloud Build, CircleCI, GitHub Actions), Git\\
\textbf{AI Infrastructure \& Perf}: vLLM, SGLang, k6, Locust\\
\textbf{Programming}: Go, Python, Bash, SQL, Nix

% Experience

\section*{Professional Experience}

\textbf{Senior Site Reliability Engineer} \hfill Jul 2025 -- Present\\
\textit{Lintasarta, Jakarta, Indonesia}

\begin{itemize}[leftmargin=*]
  \item Own the design and standardization of a centralized observability platform using Cortex (metrics), ELK stack (logs) and OpenTelemetry as the common ingestion layer for services and infrastructure.
  \item Operate production k3s-based Kubernetes clusters dedicated to observability and shared platform components.
  \item Build custom exporters in Go to collect metrics from NVIDIA GB200 devices via BMC and expose them to Cortex / Prometheus for GPU fleet monitoring.
  \item Implement GitOps with Flux and Argo CD to manage observability configuration, dashboards and alerting rules declaratively.
  \item Partner with multiple product teams to roll out common SLOs, dashboards and alerting patterns, improving incident visibility and reducing ad-hoc monitoring.
\end{itemize}

\textbf{Site Reliability Engineer} \hfill Nov 2022 -- Jun 2025\\
\textit{GDP Labs, Jakarta, Indonesia}

\begin{itemize}[leftmargin=*]
  \item Provisioned cloud infrastructure on AWS and GCP using Terraform, Ansible and Packer, enabling reproducible environments for internal and client workloads.
  \item Operated Kubernetes clusters (EKS, Kubespray) and container workloads (Docker) for microservices and platform components.
  \item Built and maintained CI/CD pipelines with Google Cloud Build and complementary tooling, automating build, test and deployment workflows.
  \item Deployed and ran GPU-based LLM inference servers using vLLM and SGLang, and executed benchmark tests with k6 to evaluate model and inference server performance.
  \item Implemented and evolved monitoring and logging stacks (Prometheus, ELK, Grafana) to reduce MTTR and improve incident investigation.
\end{itemize}

\textbf{Site Reliability Engineer Intern} \hfill Jun 2022 -- Aug 2022\\
\textit{GDP Labs, Jakarta, Indonesia}

\begin{itemize}[leftmargin=*]
  \item Automated infrastructure provisioning using Terraform and Brainboard to standardize environment creation across projects.
  \item Built CI/CD pipelines with Google Cloud Build to decrease manual deployment effort for engineering teams.
  \item Deployed VictoriaMetrics as time-series storage for metrics to support high-availability monitoring.
\end{itemize}

\textbf{Backend Engineer Student} \hfill Feb 2022 -- Jun 2022\\
\textit{Generasi Gigih}

\begin{itemize}[leftmargin=*]
  \item Completed an intensive backend program focused on Ruby, Ruby on Rails, OOP, clean code and SOLID principles.
  \item Applied unit testing, TDD and basic system design to build a backend application on Ruby on Rails.
\end{itemize}

\textbf{DevOps Engineer Intern} \hfill Oct 2021 -- Jan 2022\\
\textit{Finku, Jakarta, Indonesia}

\begin{itemize}[leftmargin=*]
  \item Implemented CI/CD pipelines on CircleCI for backend services to streamline build and deployment.
  \item Performed load testing with k6 to validate the performance of critical API endpoints.
  \item Built Grafana dashboards on top of Elasticsearch to give engineers real-time visibility into application behavior.
\end{itemize}

% Education

\section*{Education}

\textbf{Bachelor of Information Systems (S1)} \hfill 2024 -- 2026\\
\textit{Binus University, Indonesia}

\textbf{Associate Degree (D3), Computer Technology} \hfill 2019 -- 2022\\
\textit{Del Institute of Technology, Indonesia}

\end{document}
